### 2015-03-18 paper_20_sdo.tex
updates through chapter 4

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral model of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Sprial requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.8]{images/spiral_model.png}
            \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}

@@

    \subsubsection{SDLC COMMONALITIES}
        Even with the large number of SDLC models currently being used by different SDOs,
        many commonalities exist among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the implementation phase. Here are
        the common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a roadmap for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development life cycle.
        \end{description}

>>>>

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral model of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Spiral requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.8]{images/spiral_model.png}
            \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}

@@

    \subsubsection{SDLC COMMONALITIES}
        Even with the large number of SDLC models currently being used by different SDOs,
        many commonalities exist among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the implementation phase. Here are
        the common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a guideline for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development life cycle.
        \end{description}

### 2015-03-18 paper_30_measure.tex
updates the chapter 1 this work to this dissertation
updates through chapter 4

    \begin{enumerate}
        \item Identify Process Issues
        \item Select And Define Measures
        \item Integrate with Software Process
    \end{enumerate}

    This work will focus on steps 1 and 2.  The process issue is the overall
    effectiveness of the SDO.  Section \ref{sec:CRI} will cover step 2 as
    it relates to an SDO.  Step
    3 will be different for each SDO, but Section \ref{sec:SDLC-AE} provides
    a bit of guidance for storing the correct information.  It is up to the
    specific SDO to determine how and when the information is being stored.

@@

        \subsubsection{KEY RESULT INDICATOR (KRI) FOR AN SDO}
            \textit{Key Result Indicators} are measures of multiple
            activities that give a clear picture of whether the
            organization is traveling in the right direction.  Unfortunately,
            KRIs are commonly mistaken for KPIs \cite{parmenter2010}.  KRIs
            do not tell an organization what is needed to improve the 
            results.  KRIs are highly benefical for high-level management
            and not necessarily beneficial for staff working directly on 
            the software.  For
            an SDO, some possible KRIs are seen in Table \ref{tab:KRI}.

@@

        \subsubsection{PERFORMANCE INDICATOR (PI) FOR AN SDO}
            \textit{Performance Indicators} are nonfinancial performance measures
            that help a team align themselves with the organizations 
            strategy.  These are important to the organizations success, but
            they are not the key measures that will lead to drastic improvement.  They are specifically tied to a team and all staff understand
            what actions need to be taken to improve the PI.
            For an SDO, some possible PIs are seen in Table \ref{tab:PI}.

@@

        A \textit{process productivity} number is calculated based entirely
        off aspects of the SDLC and the 5 core measurements.  It is a number
        targeted at project teams working on the SDLC.

>>>>

    \begin{enumerate}
        \item Identify Process Issues
        \item Select And Define Measures
        \item Integrate with the Software Process
    \end{enumerate}

    This dissertation will focus on steps 1 and 2.  The process issue is the overall
    effectiveness of the SDO.  Section \ref{sec:CRI} will cover step 2 as
    it relates to an SDO.  Step
    3 will be different for each SDO, but Section \ref{sec:SDLC-AE} provides
    a bit of guidance for storing the correct information.  It is up to the
    specific SDO to determine how and when the information is being stored.

@@

        \subsubsection{KEY RESULT INDICATOR (KRI) FOR AN SDO}
            \textit{Key Result Indicators} are measures of multiple
            activities that give a clear picture of whether the
            organization is traveling in the right direction.  Unfortunately,
            KRIs are commonly mistaken for KPIs \cite{parmenter2010}.  KRIs
            do not tell an organization what is needed to improve the 
            results.  KRIs are highly beneficial for high-level management
            and not necessarily beneficial for staff working directly on 
            the software.  For
            an SDO, some possible KRIs are seen in Table \ref{tab:KRI}.

@@

        \subsubsection{PERFORMANCE INDICATOR (PI) FOR AN SDO}
            \textit{Performance Indicators} are non-financial performance measures
            that help a team align themselves with the organizations 
            strategy.  These are important to the organizations success, but
            they are not the key measures that will lead to drastic improvement.  They are specifically tied to a team and all staff understand
            what actions need to be taken to improve the PI.
            For an SDO, some possible PIs are seen in Table \ref{tab:PI}.

@@

        A \textit{process productivity} number is calculated based entirely
        on aspects of the SDLC and the 5 core measurements.  It is a number
        targeted at project teams working on the SDLC.
